shrimp_goby_boatnoise

### 2025-08-22 ms_boatnoise_shrimp_goby.Rmd
unifying style

#double check this
```{r}
final_df <- inner_join(goby_df, shrimp_df, by = "burrow_stage") %>% 
  mutate(
    shrimp_contact = ifelse(is.na(shrimp_contact),
                            ifelse(goby_out == 1, 0, 1 - goby_out),
                            shrimp_contact)) %>% 
  filter(site != "SITE O") %>% 
  mutate(
    parsed_date    = mdy(paste(date, "2023")),
    experiment_day = as.integer(parsed_date - min(parsed_date, na.rm = TRUE)) + 1
  )

@@

goby_out_results.table %>% 
  gt()
```

@@

#assigning a value for the baseline mean
goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control %>%
  dplyr::filter(stage == "Pre") %>%
  pull(.value)

@@

#assigning a value for the baseline mean
shrimp_out_model_estimates_control_intercept <- shrimp_out_model_estimates_control %>%
  dplyr::filter(stage == "Pre") %>%
  pull(.value)

@@

#assigning a value for the baseline mean
shrimp_contact_model_estimates_control_intercept <- shrimp_contact_model_estimates_control %>%
  dplyr::filter(stage == "Pre") %>%
  pull(.value)

@@

write_csv(model_estimates, "./2-figures/supplementary_tables/Table_S2.csv")
```

@@

write_csv(goby_out_contrasts_table, "./2-figures/supplementary_tables/Table_S3.csv")

@@

write_csv(shrimp_out_contrasts_table, "./2-figures/supplementary_tables/Table_S4.csv")

@@

write_csv(shrimp_contact_contrasts_table, "./2-figures/supplementary_tables/Table_S5.csv")
```

```{r}
table_S1 <- final_df %>%
  select(c("burrow", "stroke", "site")) |> 
  unique() |> 
  group_by(site, stroke) %>%
  summarise(n = n(), .groups = "drop") %>%
  pivot_wider(names_from = stroke, values_from = n, values_fill = 0) %>%
  mutate(Total = `control` + `4` + `2`) %>%
  arrange(site) %>%
  rename(`4-stroke` = `4`, 
         `2-stroke` = `2`, 
         Control = control)
```

@@

loo_compare(goby_out_model, cumulative_sum_goby_out_model)
```

@@

```{r}
emtrends(cumulative_sum_goby_out_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
```

@@

loo_compare(shrimp_out_model, cumulative_sum_shrimp_out_model)
```

@@

```{r}
emtrends(cumulative_sum_shrimp_out_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
```

@@

loo_compare(shrimp_contact_model, cumulative_sum_shrimp_contact_model)
```

@@

```{r}
emtrends(cumulative_sum_shrimp_contact_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
```

@@

>>>>

#double check this
```{r}
final_df <- inner_join(goby_df, shrimp_df, by = "burrow_stage") |> 
  mutate(
    shrimp_contact = ifelse(is.na(shrimp_contact),
                            ifelse(goby_out == 1, 0, 1 - goby_out),
                            shrimp_contact)) |> 
  filter(site != "SITE O") |> 
  mutate(
    parsed_date    = mdy(paste(date, "2023")),
    experiment_day = as.integer(parsed_date - min(parsed_date, na.rm = TRUE)) + 1
  )

@@

goby_out_results.table |> 
  gt()
```

@@

#assigning a value for the baseline mean
goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control |>
  dplyr::filter(stage == "Pre") |>
  pull(.value)

@@

#assigning a value for the baseline mean
shrimp_out_model_estimates_control_intercept <- shrimp_out_model_estimates_control |>
  dplyr::filter(stage == "Pre") |>
  pull(.value)

@@

#assigning a value for the baseline mean
shrimp_contact_model_estimates_control_intercept <- shrimp_contact_model_estimates_control |>
  dplyr::filter(stage == "Pre") |>
  pull(.value)

@@

write_csv(model_estimates, "./2-figures/supplementary_tables/Table_S4.csv")
```

@@

write_csv(goby_out_contrasts_table, "./2-figures/supplementary_tables/Table_S5.csv")

@@

write_csv(shrimp_out_contrasts_table, "./2-figures/supplementary_tables/Table_S6.csv")

@@

write_csv(shrimp_contact_contrasts_table, "./2-figures/supplementary_tables/Table_S7.csv")
```

```{r}
table_S1 <- final_df |>
  select(c("burrow", "stroke", "site")) |> 
  unique() |> 
  group_by(site, stroke) |>
  summarise(n = n(), .groups = "drop") |>
  pivot_wider(names_from = stroke, values_from = n, values_fill = 0) |>
  mutate(Total = `control` + `4` + `2`) |>
  arrange(site) |>
  rename(`4-stroke` = `4`, 
         `2-stroke` = `2`, 
         Control = control)
table_S1

write_csv(table_S1, "./2-figures/supplementary_tables/Table_S1.csv")
```

@@

goby_out_cumulative_loo_compare <- as.data.frame(loo_compare(goby_out_model, cumulative_sum_goby_out_model))
goby_out_cumulative_loo_compare
```

@@

```{r}
cum_sum_boat_trials_per_site_effect_goby_out <- emtrends(cumulative_sum_goby_out_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
cum_sum_boat_trials_per_site_effect_goby_out
```

@@

shrimp_out_cumulative_loo_compare <- as.data.frame(loo_compare(shrimp_out_model, cumulative_sum_shrimp_out_model))
shrimp_out_cumulative_loo_compare
```

@@

```{r}
cum_sum_boat_trials_per_site_effect_shrimp_out <- emtrends(cumulative_sum_shrimp_out_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
cum_sum_boat_trials_per_site_effect_shrimp_out
```

@@

shrimp_contact_cumulative_loo_compare <- as.data.frame(loo_compare(shrimp_contact_model, cumulative_sum_shrimp_contact_model))
shrimp_contact_cumulative_loo_compare
```

@@

```{r}
cum_sum_boat_trials_per_site_effect_shrimp_contact <- emtrends(cumulative_sum_shrimp_contact_model, ~ 1, var = "cum_sum_boat_trials_per_site", epred = TRUE, re_formula = NA)
cum_sum_boat_trials_per_site_effect_shrimp_contact
```

@@

## Additional supplementary tables

```{r}
short_label <- function(x) dplyr::recode(
  x,
  "Proportion of time gobies spent outside of the burrow"  = "Goby: time outside burrow",
  "Proportion of time shrimp spent outside of the burrow"  = "Shrimp: time outside burrow",
  "Proportion of time shrimp spent in contact with a goby" = "Shrimp–goby contact",
  .default = x
)

cumulative_loo_compare_clean <-
  bind_rows(
    goby_out_cumulative_loo_compare  |> rownames_to_column("Model") |>
      mutate(Behavioural_measure = "Proportion of time gobies spent outside of the burrow"),
    shrimp_out_cumulative_loo_compare |> rownames_to_column("Model") |>
      mutate(Behavioural_measure = "Proportion of time shrimp spent outside of the burrow"),
    shrimp_contact_cumulative_loo_compare |> rownames_to_column("Model") |>
      mutate(Behavioural_measure = "Proportion of time shrimp spent in contact with a goby")
  ) |>
  mutate(
    Behavioural_measure = short_label(Behavioural_measure),
    Model = if_else(str_detect(Model, "^cumulative_sum"), "Cumulative-sum model", "Non-cumulative model")
  ) |>
  select(
    Behavioural_measure, Model,
    elpd_loo, se_elpd_loo, looic, elpd_diff, se_diff
  ) |>
  rename(
    `Behavioural measure` = Behavioural_measure,
    `SE (elpd_loo)` = se_elpd_loo,
    `SE (elpd_diff)` = se_diff
  )

write_csv(cumulative_loo_compare_clean, "./2-figures/supplementary_tables/Table_S2.csv")

cumulative_effects_clean <-
  bind_rows(
    as.data.frame(cum_sum_boat_trials_per_site_effect_goby_out) |>
      mutate(Behavioural_measure = "Proportion of time gobies spent outside of the burrow"),
    as.data.frame(cum_sum_boat_trials_per_site_effect_shrimp_out) |>
      mutate(Behavioural_measure = "Proportion of time shrimp spent outside of the burrow"),
    as.data.frame(cum_sum_boat_trials_per_site_effect_shrimp_contact) |>
      mutate(Behavioural_measure = "Proportion of time shrimp spent in contact with a goby")
  ) |>
  mutate(Behavioural_measure = short_label(Behavioural_measure)) |>
  select(any_of(c("Behavioural_measure", "cum_sum_boat_trials_per_site.trend", "lower.HPD", "upper.HPD"))) |>
  rename(
    `Behavioural measure` = Behavioural_measure,
    `Trend per additional prior boat trial` = cum_sum_boat_trials_per_site.trend,
    `Lower 95% CrI` = lower.HPD,
    `Upper 95% CrI` = upper.HPD
  )
cumulative_effects_clean
write_csv(cumulative_effects_clean, "./2-figures/supplementary_tables/Table_S3.csv")
```
